Understanding the impacts of video-guided activities on parent-child interaction

### 2020-03-19 paper/appendix.tex
final pass with rate

---
title: "Appendix"
output: pdf_document
---

## Experiment 1 Activities

### Video A (6-11.9 months) "Pick it up"

@@

### Video B (6-11.9 months) "Animal sounds"

@@

### Video C (12-17.9 months) "Give me the toy"

@@

### Video D (12-17.9 months) "Classifying my toys"

@@

### Video E (18-23.9 months) "My toys"

@@

### Video F (18-23.9 months) "The orchestra"

@@

## Experiment 2 Activities

### Video A (12-17.9 months) "Give me the toy"

@@

### Video B (12-17.9 months) "Classifying my toys"

@@

### Video C (12-17.9 months) "Geometric shapes jigsaw puzzle"

@@

### Video D (18-23.9 months) "My toys"

@@

### Video E (18-23.9 months) "The orchestra"

@@

### Video F (18-23.9 months) "My yellow toys"

Parents are told to show their child yellow toys and to ask, "What color are they?" They are also told to give the child toys of different colors, to ask them to only play with the yellow ones, and to praise the child after they do so.

Props: blue car, yellow car, yellow block, red block, blue block, green block

>>>>

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\section{}
\hypertarget{experiment-1-activities}{%
\subsection{Experiment 1 Activities}\label{experiment-1-activities}}

\hypertarget{video-a-6-11.9-months-pick-it-up}{%
\subsubsection{Video A (6-11.9 months) ``Pick it
up''}\label{video-a-6-11.9-months-pick-it-up}}

@@

\hypertarget{video-b-6-11.9-months-animal-sounds}{%
\subsubsection{Video B (6-11.9 months) ``Animal
sounds''}\label{video-b-6-11.9-months-animal-sounds}}

@@

\hypertarget{video-c-12-17.9-months-give-me-the-toy}{%
\subsubsection{Video C (12-17.9 months) ``Give me the
toy''}\label{video-c-12-17.9-months-give-me-the-toy}}

@@

\hypertarget{video-d-12-17.9-months-classifying-my-toys}{%
\subsubsection{Video D (12-17.9 months) ``Classifying my
toys''}\label{video-d-12-17.9-months-classifying-my-toys}}

@@

\hypertarget{video-e-18-23.9-months-my-toys}{%
\subsubsection{Video E (18-23.9 months) ``My
toys''}\label{video-e-18-23.9-months-my-toys}}

@@

\hypertarget{video-f-18-23.9-months-the-orchestra}{%
\subsubsection{Video F (18-23.9 months) ``The
orchestra''}\label{video-f-18-23.9-months-the-orchestra}}

@@

\hypertarget{experiment-2-activities}{%
\subsection{Experiment 2 Activities}\label{experiment-2-activities}}

\hypertarget{video-a-12-17.9-months-give-me-the-toy}{%
\subsubsection{Video A (12-17.9 months) ``Give me the
toy''}\label{video-a-12-17.9-months-give-me-the-toy}}

@@

\hypertarget{video-b-12-17.9-months-classifying-my-toys}{%
\subsubsection{Video B (12-17.9 months) ``Classifying my
toys''}\label{video-b-12-17.9-months-classifying-my-toys}}

@@

\hypertarget{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}{%
\subsubsection{Video C (12-17.9 months) ``Geometric shapes jigsaw
puzzle''}\label{video-c-12-17.9-months-geometric-shapes-jigsaw-puzzle}}

@@

\hypertarget{video-d-18-23.9-months-my-toys}{%
\subsubsection{Video D (18-23.9 months) ``My
toys''}\label{video-d-18-23.9-months-my-toys}}

@@

\hypertarget{video-e-18-23.9-months-the-orchestra}{%
\subsubsection{Video E (18-23.9 months) ``The
orchestra''}\label{video-e-18-23.9-months-the-orchestra}}

@@

\hypertarget{video-f-18-23.9-months-my-yellow-toys}{%
\subsubsection{Video F (18-23.9 months) ``My yellow
toys''}\label{video-f-18-23.9-months-my-yellow-toys}}

Parents are told to show their child yellow toys and to ask, ``What
color are they?'' They are also told to give the child toys of different
colors, to ask them to only play with the yellow ones, and to praise the
child after they do so.

Props: blue car, yellow car, yellow block, red block, blue block, green
block
\end{appendix}
